A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-25 0_main.tex
Tim: Spell check

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness.
An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.

>>>>

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness.
An accurate dense filling is especially important for thin parts such as casings for electronics, blow molding prototypes, (architectural) models, and microstructures.

### 2019-08-25 1_intro.tex
Tim: Spell check

\section{Introduction}
3D printing enables the fabrication of complex geometry under few design constraints compared to conventional fabrication techniques.
Recent developments have seen a rapid growth in both the use and capabilities of desktop 3D printing systems.
%The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures.
Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{}, topology optimized structures~\cite{} and infill structures~\cite{}.
Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude a contour following print path,
because the positiong and shape of the toolpath can be controled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfll} areas.
See \cref{intro_wedge}(top).
Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
Some such toolpath generation techniques have already been developed.

>>>>

\section{Introduction}
3D printing enables the fabrication of complex geometry under few design constraints compared to conventional fabrication techniques.
Recent developments have seen a rapid growth in both the use and capabilities of desktop 3D printing systems.
%The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{}, topology optimized structures~\cite{} and infill structures~\cite{}.
Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude a contour following print path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfill} areas.
See \cref{intro_wedge}(top).
Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
Some such toolpath generation techniques have already been developed.

### 2019-08-25 4_method.tex
Tim: Spell check

\begin{figure}\centering
\setlength{\figwidth}{0.19\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
\caption{Polygon Domains}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the inout shape polygons.
}
\label{skeletonization_comparison}
\end{figure}

@@

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
A node in the ST can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.
\fi

@@

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a flattening operator which maps a feature diameter to a bead count: $f: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framewotk the function $b$ is determined by a beading strategy.

@@

For our example we linearly map the $R$ values using a multiplication factor of $d/n$:
\begin{align*}
w_i &= d/n  \\
l_i &= d / n (i + \nicefrac12)
\end{align*}
An example beading is visualzied in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{sources/method/beading_interpolation_v2.pdf}
\caption{
Interpolation between two beadings $B^V$ and $B^W$ with a ratio $x$ results in a beading $B^x$.
Distances between the thick black lines constitute diameters $d$,
the toolpath locations are visualized as dots,
the widths are visualized as bidirection arrows
and the middle is highlighted in red.
}
\label{beading_interpolation}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings togenerate junctions along trapezoids.
\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support edges.
No junctions will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{junction_placement}
\end{figure}

@@

Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
Such intersections cause overextrusion because the nozzle passes the location multiple times.
In order to reduce the amount of overextrusion of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}$ is some ration between $0$ and $1$.
We do this for all polylines until only two outward toolpath segments remain, which constitute a single pass over the junction.
See \cref{polyline_reduction}.

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.45\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_unreduced.pdf}
\caption{No reduction}
\end{subfigure}
\begin{subfigure}{0.45\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_reduced.pdf}
\caption{Reduction}
\end{subfigure}
\caption{
Reducing polyline toolpaths away from intersections in order to prevent overextrusion.
Toolpath locations in black, underextrusion in blue, overextrusion in red and orange and normal extrusion in grey.
Intersections result in overextrusion, so we remove parts of the polylines at intersections.
}
\label{polyline_reduction}
\end{figure}

>>>>

\begin{figure}\centering
\setlength{\figwidth}{0.19\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
\caption{Polygon Domains}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the input shape polygons.
}
\label{skeletonization_comparison}
\end{figure}

@@

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
A node in the ST can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore not significant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.
\fi

@@

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a flattening operator which maps a feature diameter to a bead count: $f: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framework the function $b$ is determined by a beading strategy.

@@

For our example we linearly map the $R$ values using a multiplication factor of $d/n$:
\begin{align*}
w_i &= d/n  \\
l_i &= d / n (i + \nicefrac12)
\end{align*}
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{sources/method/beading_interpolation_v2.pdf}
\caption{
Interpolation between two beadings $B^V$ and $B^W$ with a ratio $x$ results in a beading $B^x$.
Distances between the thick black lines constitute diameters $d$,
the toolpath locations are visualized as dots,
the widths are visualized as bidirectional arrows
and the middle is highlighted in red.
}
\label{beading_interpolation}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings to generate junctions along trapezoids.
\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support edges.
No junctions will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{junction_placement}
\end{figure}

@@

Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
Such intersections cause overfill because the nozzle passes the location multiple times.
In order to reduce the amount of overfill of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}$ is some ration between $0$ and $1$.
We do this for all polylines until only two outward toolpath segments remain, which constitute a single pass over the junction.
See \cref{polyline_reduction}.

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.45\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_unreduced.pdf}
\caption{No reduction}
\end{subfigure}
\begin{subfigure}{0.45\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_reduced.pdf}
\caption{Reduction}
\end{subfigure}
\caption{
Reducing polyline toolpaths away from intersections in order to prevent overfill.
Toolpath locations in black, underfill in azure and overfill in orange.
Intersections result in overfill, so we remove parts of the toolpaths at intersections.
}
\label{polyline_reduction}
\end{figure}

### 2019-08-25 5_generalization.tex
Tim: Spell check

Because the peripheral height adjustment was described in terms of a mapping from radial distances to junctions rather than adjusting the heights of peripheral nodes,
we can introduce non-linear mappings without refining the surface mesh.
In the simplified geometrical conceptualization of our technique we can introduce different distributions of bead widths from the center outward, by making the contours of the cones curved.
If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thsu their width becomes larger when going inward.
In order for the simplified geometrical approach to capture such curved shapes it would have to perform mesh refinement.
However, our approach bypasses the peripheral height adjustment and directly generates the radial distances at the slicing heights, which means our technique generalized effortlessly.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using the naive strategy will still hold approximately.

>>>>

Because the peripheral height adjustment was described in terms of a mapping from radial distances to junctions rather than adjusting the heights of peripheral nodes,
we can introduce non-linear mappings without refining the surface mesh.
In the simplified geometrical conceptualization of our technique we can introduce different distributions of bead widths from the center outward, by making the contours of the cones curved.
If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thus their width becomes larger when going inward.
In order for the simplified geometrical approach to capture such curved shapes it would have to perform mesh refinement.
However, our approach bypasses the peripheral height adjustment and directly generates the radial distances at the slicing heights, which means our technique generalized effortlessly.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the naive strategy will still hold approximately.

### 2019-08-25 6_validation.tex
Tim: Spell check

\section{Validation}
In order to test our framework, we have assembled a dataset of different types of 3D models, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the dataset and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the dataset was recorded for the "Inward distributed" and "Naive" strategy. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
The overfill and underfill areas as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the dataset.

@@

\caption{
Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

@@

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the depositioning control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading strategy than the other strategies.

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}

>>>>

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the data set was recorded for the "Inward distributed" and "Naive" strategy. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

@@

\caption{
Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the data set.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

@@

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading strategy than the other strategies.

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the naive strategy, center deviation strategy and the inward distributed strategy.
The naive and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deviation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}

### 2019-08-25 8_discussion.tex
Tim: Spell check

\subsection{Limitations}
In the beading strategies we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While ching the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
Our strategies require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

>>>>

\subsection{Limitations}
In the beading strategies we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
Our strategies require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
